Online {\IterComp}

### 2017-09-16 prof.tex
FIXEdME
make formulae penetrable

Afterwards, the algorithm propagates the known edge flows, inferring
the symbolic expressions in the unknown edge flows.
This is achieved by performing a bottom-up propagation from the trivially known
edge flows (in red) by applying the Kirchhoff's first law, i.e.,
for each vertex with a single unknown edge flow, we compute the difference between
the known incoming edge flows by the known outgoing edge flows.
Formally,
for each vertex $u\in G$, in a post-order traversal of the spanning tree,
we can use the Kirchhoff's first law and apply the following operations
in a symbolic fashion:
\[
\Sigma^+_u = \sum_{v\in N^+(u)} D_{(u,v)}
\]
\[
\Sigma^-_u = \sum_{v\in N^-(u)} D_{(v,u)}
\]
\[
\forall v\in N^+(u):  D_{(u,v)} \gets
\begin{cases}
    D_{(u,v)} & \quad \text{if $D_{(u,v)}\neq 0$}\\
    \Sigma^-_u - \Sigma^+_u       & \quad \text{otherwise}
\end{cases}
\]
\[
\forall v\in N^-(u):  D_{(v,u)} \gets
\begin{cases}
    D_{(v,u)} & \quad \text{if $D_{(v,u)}\neq 0$}\\
    \Sigma^+_u - \Sigma^-_u       & \quad \text{otherwise}
\end{cases}
\]

\paragraph{Composing the aggregated value of the probes:}
If $x$ is a symbolic expression, then $\kappa_P(x)$ represents the coefficient
of the term $P$ in $x$.
In our case, $\kappa_P(x)$ will belong to the set $\{-1,0,1\}$.
Then, for all probes $P$:
\[
\omega(P) = \sum_{u\in G} \kappa_P(\Sigma^+_u)w(u)
\]

@@

For our experiments, we implemented two solvers for the 0-1 Knapsack problems: an optimal but potentially slow brute-force solver and a
greedy heuristic based on sorting the items~\citep{dantzig57}. We use the brute-force solver with a small number of probes, less than
\FIXME{30}, and the greedy heuristic otherwise.

@@

The \WCRelaxLower relaxation provides hard guarantees that error will remain below the chosen threshold but in many cases these
guarantees are too conservative. It assumes that each loop will always execute the path with the minimum amount of work
possible, which might be orders of magnitude less than the work actually performed. In such cases, we remove too few probes and have little
effect on the profiling overhead, while the actual relative error in our work estimation is negligible. To avoid this problem, we
propose a more aggressive approach that operates on the probes from whole program at once.

>>>>

Afterwards, the algorithm propagates the known edge flows, inferring
the symbolic expressions in the unknown edge flows.
This is achieved by performing a bottom-up propagation from the trivially known
edge flows (in red) by applying the Kirchhoff's first law, i.e.,
for each vertex with a single unknown edge flow, we compute the difference between
the known incoming edge flows by the known outgoing edge flows.
Formally,
for each vertex $u\in G$, following a post-order traversal of the spanning tree,
the Kirchhoff's first law is applied as the following symbolic operations:
First, sum all the out-going edge flows
\[
%\Sigma^+_u = \sum_{v\in N^+(u)} D_{(u,v)}
\mathrm{SumOut}(u): \sum_{v\in N^+(u)} D_{(u,v)}
\]
and then sum all the in-coming edge flows
\[
%\Sigma^-_u = \sum_{v\in N^-(u)} D_{(v,u)}
\mathrm{SumIn}(u): \sum_{v\in N^-(u)} D_{(v,u)}
\]
For all out-going neighbor $v\in N^+(u)$,
\[
%\forall v\in N^+(u):  D_{(u,v)} \gets
D_{(u,v)} \gets
\begin{cases}
    D_{(u,v)} & \!\!\!\quad \text{if $D_{(u,v)}\neq 0$}\\
    \mathrm{SumIn}(u) - \mathrm{SumOut}(u)       & \!\!\!\quad \text{otherwise}
\end{cases}
\]
For all in-coming neighbor $v\in N^-(u)$,
\[
%\forall v\in N^-(u):  D_{(v,u)} \gets
D_{(v,u)} \gets
\begin{cases}
    D_{(v,u)} & \!\!\!\quad \text{if $D_{(v,u)}\neq 0$}\\
    \mathrm{SumOut}(u) - \mathrm{SumIn}(u)       & \!\!\!\quad \text{otherwise}
\end{cases}
\]

\paragraph{Composing the aggregated value of the probes:}
If $x$ is a symbolic expression, then $\kappa_P(x)$ represents the coefficient
of the term $P$ in $x$.
In our case, $\kappa_P(x)$ will belong to the set $\{-1,0,1\}$.
Once all the edge flows are known, then, 
for all probes $P$, the amount of work associated
with probe $P$ is:
\[
%\omega(P) = \sum_{u\in G} \kappa_P(\Sigma^+_u)w(u)
\omega(P) = \sum_{u\in G} \kappa_P(\mathrm{SumOut}(u))w(u)
\]

@@

For our experiments, we implemented two solvers for the 0-1 Knapsack problems: an optimal but potentially slow brute-force solver and a
greedy heuristic based on sorting the items~\citep{dantzig57}. We use the brute-force solver with a small number of probes, less than
20, and the greedy heuristic otherwise.

@@

The \WCRelaxLower relaxation provides hard guarantees that error will remain below the chosen threshold but in many cases these
guarantees are too conservative. It assumes that each loop will always execute the path with the minimum amount of work
possible, which might be orders of magnitude less than the work actually performed. In such cases, we remove too few probes and have little
effect on the profiling overhead, while the actual relative error in our work estimation is negligible. To avoid this problem, we
propose a more aggressive approach that operates on the probes from the whole program at once.
